### 2019-09-14 2019_neurips_vigil/intro.tex
intro

Integration of vision and language in deep neural network models allows learning joint representations of objects, concepts, and relations.  In addition to multimodal learning, visual grounding of language is another opportunity that the AI community is excited about, especially in the context of Harnad's "symbol grounding problem" \cite{harnad2003symbol}.

Starting with the VQA dataset \cite{}, many tasks have emerged in the past several years\cite{mogadala2019trends}.  Since the conception of the VQA benchmark, visual reasoning is the main emphasis in these tasks, which can be expressed in language. Visual reasoning mainly deals with the comparison of object attributes, counting and other relational questions.
In contrast to VQA, which comes with static image and question pairs, an emerging field is Video QA \cite{} that introduced the temporal aspect in the visual input.  Video input provides another opportunity to test system's ability to deal with temporal relations and reasoning.  As evident from human cognition, attention and memory are the key components that are required to solve these problems, which need to process spatial and temporal information.

The ability to deal with time is a challenge also for natural language processing (NLP), for example in question answering (QA) systems and in dialog applications.  The current NLP solutions, in certain problem settings, can work around this challenge by processing the entire text input and reason over it using attention \cite{vaswani2017attention} or other mechanisms. For example, Memory Networks \cite{weston2015towards}, solves the bAbI reasoning task by processing the supporting facts all at once, which reside in memory and available to provide answers. Similarly, in Visual Dialog~\cite{das2017visual} the system keeps the whole history of the dialog in memory.  In real-time dialog or video QA, there may not be such opportunity or the system may be forced to record the whole history which is not always feasible.  Video reasoning datasets such as SVQA (Synthetic Video Question Answering)~\cite{song2018explore} and COG \cite{yang2018dataset} have limited number of frames (e.g. 4-16 frames), and therefore manageable by the neural net models to process and represent all of the visual information. According to\cite{song2018explore} the authors extracted visual features from each clip and aggregated features of all clips from one video to form a sequential video representation.
These solutions may demonstrate high accuracy and apply to specific problems, however, generalization to arbitrary length video sequences will be problematic.  Such approaches also differ from the human cognitive strategies.  Humans have the ability to selectively pay attention and store important items or events in memory based on their goals.  Working memory and episodic memory systems are responsible for this remarkable ability.

@@

\subsection{Contributions}

\begin{itemize}
\item \textbf{Time aspect}:
\begin{itemize}
\item Learning the temporal association - grounding the time-related words with meaning
\item Learning the concept of time
\item time context being by-product of gates
\end{itemize}

\item Visual Grounding:
\begin{itemize}
\item Learning complex, multi-step reasoning that involves grounding of words and visual representations/objects
\item 
\end{itemize}
\item \textbf{Selective Attention Memory}:
\begin{itemize}
\item updating the memory content only with relevant visual information depending on the temporal context
\item content based and location based addressing for reading and writing
\item new memory interface/gating designed in such a way enabling the model to control the flow of current visual information and content of the memory in a selective way

\end{itemize}
\end{itemize}

>>>>

Integration of vision and language in deep neural network models allows the system to learn joint representations of objects, concepts, and relations.  Potentially, this approach can address Harnad's "symbol grounding problem" \cite{harnad2003symbol} and lead to visually grounded language learning.
%In addition to multimodal learning, visual grounding of language is another opportunity that the AI community is excited about, especially in the context of Harnad's "symbol grounding problem" \cite{harnad2003symbol}.

Starting with the Visual Question Answering (VQA) dataset \cite{}, many tasks that integrate vision and language have emerged in the past several years\cite{mogadala2019trends}.  As a departure from the simpler vision tasks like classification and object detection, visual reasoning has become the core emphasis in these tasks. Visual reasoning mainly deals with the comparison of object attributes, counting and other relational questions.

In contrast to VQA, which comes with static image and question pairs, another emerging direction is Video QA \cite{}, which introduces the aspect of time.  In addition to spatial reasoning, video input provides an opportunity to work on temporal relations and reasoning.  As evident from human cognition, attention and memory are the key competencies required to solve these problems, and unsurprisingly, the AI research is rapidly growing in these areas.

The ability to deal with time can pose a challenge for natural language processing (NLP) as well; for instance, in question answering (QA) and dialog applications.  The current NLP solutions, in certain problem settings, can work around this challenge by processing the entire text input and reason over it multiple times using attention \cite{vaswani2017attention} or other mechanisms. For example, solutions to the bAbI reasoning task (e.g. Memory Networks \cite{weston2015towards}), typically involve processing the supporting facts all at once, which reside in memory and available to provide answers. Similarly, in Visual Dialog~\cite{das2017visual} the system keeps the whole history of the dialog in memory.  In real-time dialog or video QA, there may not be such an opportunity to have the question and entire input all at once in the beginning.

Video reasoning datasets such as SVQA (Synthetic Video Question Answering)~\cite{song2018explore} and COG \cite{yang2018dataset} have limited number of frames (e.g. 4-16 frames), and therefore manageable by the neural net models to process and represent all of the visual information.  As an example, according to\cite{song2018explore} the authors extracted visual features from each frame and aggregated features of all clips from one video to form a sequential video representation.
These solutions may demonstrate high accuracy, however, generalization to arbitrary length video sequences will be problematic.  Such approaches also differ from the human cognitive strategies.  Humans have the ability to selectively pay attention and store salient items or events in memory based on their goals.  Working memory and episodic memory systems are responsible for this remarkable ability.

@@

\subsection{Contributions}
This work have attempted to address the issues mentioned above and propose a new model that can dynamically process video input frame-by-frame, reason over images and remember the salient concepts to answer questions.  We have tested this model on the COG dataset \cite{yang2018dataset} and compared to the baseline results.  Our results indicate that the model is capable of:
%\begin{itemize}
%\item \textbf{Time aspect}:
\begin{itemize}
\item Learning the temporal association - grounding the time-related words with meaning
%\item Learning the concept of time
%\item time context being by-product of gates
%\end{itemize}

\item Learning complex, multi-step reasoning that involves grounding of words and visual representations of objects/attributes
%\begin{itemize}
%\item Learning complex, multi-step reasoning that involves grounding of words and visual representations/objects
\item Selectively control the flow of information to and from the memory to answer questions
%\end{itemize}
%\item \textbf{Selective Attention Memory}:
%\begin{itemize}
\item Updating the memory content only with relevant visual information depending on the temporal context
%\item content based and location based addressing for reading and writing
%\item new memory interface/gating designed in such a way enabling the model to control the flow of current visual information and content of the memory in a selective way

\end{itemize}
%\end{itemize}
